### 2019-07-08 manuscript.tex
A few more comments.

Our main response variables were woman's \jdcmt{I don't think this work adds anything; behavioural} reported intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.  \jdcmt{You are describing just some predictors; The predictors selected} \jdcmt{I don't know what is being conveyed here, can we lose it? based on literature (e.g., aforementioned above)} were woman's FGC status and beliefs about FGC benefits (see supp for the benefit questionnaire).  The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of benefits associating with fgc practice. We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s self-awareness would moderate \cf{wording} their intention of FGC practice \cfonly{cites of feminist theory on fgc}. Other socio-demographic variables included were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use and residence (urban vs. rural) in addition to country.  Media use and gender awareness were scored.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

@@

\jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  But as J said, it is too hard! } %``explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. `` \cite{Hayf05}
\cfcmt{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788)}
\cfcmt{Regarding FGC benefits modules, there were 9 questions.  Keya had all the 9, Mali and SL 7 (missing promiscuity and STD), NG 8, missing STD).  Should we drop STD since 3 out of 4 missed this variable?}
\cfonly {in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).

\subsubsection{Statistical Model}\label{statistical-model}

We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.  The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.  
We subtracted respondent (-1) from the cluster when testing the community effect \cfjdml{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}

\cfcmt{Do we explain conveyance of uncertainty and data sampling?}

\cfcmt{Our response ARE categorical not binary; AND still need to explain why ethnicity is a random effect. AND media use was supposed to be incorporated as a random factor at the country level, based on the assumption that media content likely varied among countries.}

@@

@@

Baseline socio-demographic and sample characteristics are shown in figure x.  The prevalence of FGC are 31.8\%, 88.6\%, 45.9\% and 91.0\%, and 15.5\%, 73.9\%, 20.6\% and 65.5\% of the samples thought FGC should be continued in Kenya, Mali, Nigeria and Sierra Leon accordingly.

>>>>

Our main response variables were woman's \jdcmt{I don't think this work adds anything; behavioural} reported intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.  \jdcmt{You are describing just some predictors but it sounds like all; The predictors selected} \jdcmt{I don't know what is being conveyed here, can we lose it? based on literature (e.g., aforementioned above)} were woman's FGC status and beliefs about FGC benefits (see supp for the benefit questionnaire).  \jdcmt{This seems very wordy: The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify} the strength of benefits associating with fgc practice. We also included gender awareness (see WHERE for questions of gender awareness proxy) in our models to test if women’s self-awareness would moderate \cf{wording} their intention of FGC practice \cfonly{cites of feminist theory on fgc}. Other socio-demographic variables included were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use and residence (urban vs. rural) in addition to country.  Media use and gender awareness were scored.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

@@

\jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  But as J said, it is too hard! } %``explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. `` \cite{Hayf05}
\cfcmt{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788)}
\jdcmt{What happened to the text about what we are actually doing with 
\cfcmt{Regarding FGC benefits modules, there were 9 questions.  Keya had all the 9, Mali and SL 7 (missing promiscuity and STD), NG 8, missing STD).  Should we drop STD since 3 out of 4 missed this variable?}
\cfonly {in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).  
\subsubsection{Statistical Model}\label{statistical-model}

We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.  The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.  
\jdcmt{Did we do anything weird here with intercepts? Why do we have different intercepts with different models?} We subtracted respondent (-1) from the cluster when testing the community effect \cfjdml{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).} \jdcmt{No, we don't have to worry about clusters with only one sample.}

\cfcmt{Do we explain conveyance of uncertainty and data sampling?}
\jdcmt{Can you explain this question?}

\cfcmt{Our response ARE categorical not binary; AND still need to explain why ethnicity is a random effect. AND media use was supposed to be incorporated as a random factor at the country level, based on the assumption that media content likely varied among countries.}
\jdcmt{Not sure what any of this is about. Our response are ordinal, and binary is an example of ordinal. I don't think there needs a big problem with using ethnicity as a random effect, or with explaining it. I kind of feel we are going in circles because you're not happy with it -- but do you have a solution?}

@@

\jdcmt{Why on request? I always distrust that from others. Any objection to publishing the code?}

@@

Baseline socio-demographic and sample characteristics are shown in figure x.  The prevalence of FGC are 31.8\%, 88.6\%, 45.9\% and 91.0\%, and 15.5\%, 73.9\%, 20.6\% and 65.5\% of the samples thought FGC should be continued in Kenya, Mali, Nigeria and Sierra Leon accordingly. \jdcmt{This \P is inaesthetic. If the figure is not clear enough, we could have a table? Or else, we could just give ranges here?}
